What's in a Name? \\ Linear Temporal Logic \\ Literally Represents Time Lines

### 2023-08-28 paper/main.tex
consistency

%\section{Theoretical Analyses} \label{sec:analysis}
\section{``If we are true to ourselves, we can not be false to anyone\textsuperscript{\textsection}''}
\label{sec:analysis}
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{William Shakespeare, \emph{Hamlet}}
\endgroup

@@

%\section{Tool showcase}
\section{``Be great in act, as you have been in thought\textsuperscript{\textsection}''}
\label{sec:tool-showcase}
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{William Shakespeare, \emph{King John}}
\endgroup
To demonstrate using \tool, we present three examples, one from a real-world model checking exercise from Zhao and Rozier~\cite{ZR14}, one from a randomly generated LTL formula, and one that specifically shows the applicability of \tool\ to specification validation.

@@

\section{Thought is free\textsuperscript{\textsection}: Artifact availability}
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{William Shakespeare, \emph{The Tempest}}
\endgroup
The tool we present in this paper is available at
\[
    \texttt{\url{https://github.com/EULIR/ltl-explainability}}
\]
which comes with two command-line tools, \texttt{ltl2regex} and \tool. The specific usage of the tool can be found  \href{https://github.com/EULIR/ltl-explainability#usage}{here}.

>>>>

%\section{Theoretical Analyses} \label{sec:analysis}
\section{Theoretical Analyses: ``If we are true to ourselves, we can not be false to anyone\textsuperscript{\textsection}''}
\label{sec:analysis}
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{William Shakespeare, \emph{Hamlet}}
\endgroup

@@

%\section{Tool showcase}
\section{Tool Showcase: ``Be great in act, as you have been in thought\textsuperscript{\textsection}''}
\label{sec:tool-showcase}
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{William Shakespeare, \emph{King John}}
\endgroup
To demonstrate using \tool, we present three examples, one from a real-world model checking exercise from Zhao and Rozier~\cite{ZR14}, one from a randomly generated LTL formula, and one that specifically shows the applicability of \tool\ to specification validation.

@@

\section{Artifact Availability: ``Thought is free\textsuperscript{\textsection}" }
\begingroup\renewcommand\thefootnote{\textsection}
\footnotetext{William Shakespeare, \emph{The Tempest}}
\endgroup
The tool we present in this paper is available at
\[
    \texttt{\url{https://github.com/EULIR/ltl-explainability}}
\]
which comes with two command-line tools, \texttt{ltl2regex} and \tool. The specific usage of the tool can be found  \href{https://github.com/EULIR/ltl-explainability#usage}{here}.
